RDF Constraint Types to Ensure High Data Quality

### 2015-04-29 paper/paper7/paper7.tex
feedback
evaluation

In this paper, we formulate 213 constraints of 53 different types on four different vocabularies (Disco, QB, SKOS, PHDD) and classify them according to the complexity level of their type and their severity level. For 114 of these constraints, we evaluate the data quality of 15,694 datasets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.

@@

\begin{enumerate}
	\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$). 
  \item Second, several SBE domain experts of the vocabularies \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} evaluated the correctness (i.e., the gold standard) of all $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraints and therefore the generic applicability of the developed classification system of constraint types and constraints. 
%i.e., the gold standard, has been proved by multiple SBE domain experts.
  \item Third, we exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
\end{enumerate}
We validated 
9,990 / 3,775,983,610 (\emph{QB}),
4,178 / 477,737,281 (\emph{SKOS}), and 
1,526 / 9,673,055 (\emph{Disco}) data sets / triples using the \emph{RDF Validator} in batch mode.
That are more than 4.2 billion triples and 15 thousand data sets.
We validated, i.a., 
(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics (ABS)},
the \emph{European Central Bank (ECB)}, and the
\emph{Organisation for Economic Co-operation and Development (OECD)},
(2) \emph{SKOS} thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
the \emph{STW Thesaurus for Economics}, and the
\emph{Thesaurus for the Social Sciences (TheSoz)}, and
(3) \emph{Disco} data sets provided by the \emph{Microdata Information System (Missy)}, 
the \emph{DwB Discovery Portal}, the
\emph{Danish Data Archive (DDA)}, and the
\emph{Swedish National Data Service (SND)}.
We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as second appendix of this paper) 
in which we describe the comprehensive evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.

@@

The majority (48 $\equiv$ 58.5\%) of the overall 82 $\mathcal{CT}$ constraint types are $\mathcal{CT}_{B}$ whose constraints can therefore be derived from vocabularies without any effort.
Among $\mathcal{CT}_{B}$, two-thirds (34 $\equiv$ 70.8\%) are $\mathcal{C}_B ^{\mathcal{R}}$, i.e., constraint types for which reasoning may be performed prior to validation, and one third (14 $\equiv$ 29.2\%) are $\overline{\mathcal{C}_B ^{\mathcal{R}}}$, i.e., constraint types for which reasoning does not make any sense.
A quarter (20 $\equiv$ 24.4\%) of all constraint types are $\mathcal{CT}_{S}$ and a sixth (14 $\equiv$ 17.1\%) are $\mathcal{CT}_{C}$.

\begin{table}[H]
		\scriptsize
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%    \\  \cmidrule{2-7}
    \\       \textbf{Criteria}
           & \textbf{\emph{Disco}}
           & \textbf{\emph{QB}}
					 & \textbf{\emph{SKOS}}
					 & \textbf{Total}
    \\ \midrule
		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
		%\hline
		\emph{CT} & 52 & 20 & 15 & 53 \\
		\hline
		$\mathcal{CT}_{C}$ & 9 (17.3\%) & 2 (10\%) & 2 (13.3\%) & 9 (17\%) \\
		$\mathcal{CT}_{S}$ & 16 (30.8\%) & 3 (15\%) & 4 (26,7\%) & 16 (30.2\%) \\
		$\mathcal{CT}_{B}$ & 27 (\textbf{51.9\%}) & 15 (\textbf{75\%}) & 9 (\textbf{60\%}) & 28 (\textbf{52.8\%}) \\
		\hline
		$\mathcal{C}_B ^{\mathcal{R}}$ & 18 (34.6\%) & 9 (45\%) & 4 (26.7\%) & 19 (35.9\%) \\
		$\overline{\mathcal{C}_B ^{\mathcal{R}}}$ & 9 (17.3\%) & 6 (30\%) & 5 (33.3\%) & 9 (17\%) \\
    \bottomrule
    \end{tabular}
    %\\ \emph{C (constraints), CT (constraint types)}
    \caption{Evaluation - Constraint Types}
		\label{tab:evaluation-constraint-types}
    \end{center}
\end{table}

%Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
We defined constraints of 53 distinct $\mathcal{CT}$ constraint types (see table \ref{tab:evaluation-constraint-types}).
More than the half of them are $\mathcal{CT}_{B}$, more than a third $\mathcal{C}_B ^{\mathcal{R}}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
For \emph{Disco}, \emph{QB}, and \emph{SKOS}, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
(for \emph{QB} even three quarters).
\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.

\begin{table}[H]
		\scriptsize
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%    \\  \cmidrule{2-7}
    \\       \textbf{Criteria}
           & \textbf{\emph{Disco}}
           & \textbf{\emph{QB}}
					 & \textbf{\emph{SKOS}}
					 & \textbf{Total}
    \\ \midrule
		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
		%\hline
		\emph{C} & 143 (67.1\%) & 35 (16.4\%) & 35 (16.4\%) & 213 \\
		\hline
		\emph{C (}$\mathcal{CT}_{C}$\emph{)} & 37 (25.9\%) & 13 (37.1\%) & 13 (\textbf{37.1\%}) & 63 (29.6\%) \\
		\emph{C (}$\mathcal{CT}_{S}$\emph{)} & 28 (19.6\%) & 3 (8.6\%) & 12 (\textbf{34.3\%}) & 43 (20.2\%) \\
		\emph{C (}$\mathcal{CT}_{B}$\emph{)} & 78 (\textbf{54.6\%}) & 19 (\textbf{54.3\%}) & 10 (\textbf{28.6\%}) & 107 (\textbf{50.2\%}) \\
		%\hline
		%\emph{C (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 67 (46.9\%) & 13 (37.1\%) & 4 (11.4\%) & 84 (39.4\%) \\
		%\emph{C (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 11 (7.7\%) & 6 (17.1\%) & 6 (17.1\%) & 23 (10.8\%) \\
		\hline
		\emph{C ($\mathcal{SL}_{0}$)} & 75 (\textbf{52.5\%}) & 4 (11.4\%) & 21 (\textbf{60\%}) & 100 (\textbf{46.9\%}) \\
		\emph{C ($\mathcal{SL}_{1}$)} & 10 (7\%) & 3 (8.6\%) & 5 (14.3\%) & 18 (8.5\%) \\
		\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.6\%) & 28 (\textbf{80\%}) & 9 (25.7\%) & 95 (\textbf{44.6\%}) \\
    \bottomrule
    \end{tabular}
    %\\ \emph{C (constraints), CT (constraint types)}
    \caption{Evaluation - Constraints}
		\label{tab:evaluation-constraints}
    \end{center}
\end{table}

Half of the overall 213 $\mathcal{CT}$ constraints are $\mathcal{CT}_{B}$ constraints (almost 40\% $\mathcal{C}_B ^{\mathcal{R}}$) (see table \ref{tab:evaluation-constraints}).
This is not surprising as more than the half of the instantiated constraints types are $\mathcal{CT}_{B}$ constraint types.
More than 50\% of the \emph{Disco} and \emph{QB} constraints are $\mathcal{CT}_{B}$ constraints.
The \emph{SKOS} constraints, on the other side, are equally assigned to the three disjoint constraint type sets. 
\emph{SBE} domain experts associated almost the half of the constraints with the severity levels $\mathcal{SL}_{0}$ (\emph{informational}) (47\%) and $\mathcal{SL}_{2}$ (\emph{error}) (45\%);
only 8.5\% are $\mathcal{SL}_{1}$ (\emph{warning}) constraints.
The violation of 80\% of the \emph{QB} constraints is very serious ($\mathcal{SL}_{2}$).
More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are assigned to the weakest default severity level ($\mathcal{SL}_{0}$).

@@

@@

\tb{difference between 0\% and 78.6\%}
\tb{basic constraints sind bei etablierten vokabularen publitierte datensätze werden eingehalten hohe datenqualität / schwerwiegende constraintverletzungen treten kaum auf / schwere constraints sind in idesen vielen daten nicht auf / disco ist in beiden fällen anders / erheblichen anteil von schwersten constraint verletzungen / disco neues vokabular das noch daten gelten noch einenm draft von disco oder hat disco nicht verstanden schnlechtere daten als entabliete vokabulare / es ist sinnvoll sprachen zu entwickeln komplexere constraints auszudrücken / simple und vocabulary können heute schon sehr gut beschrieben werden / wir wünschen und dass es komplexere constraint languages gibt mit denen complex constraints besser abgebildet werden können / deulticherer verbesserung in der datenualitt wenn wir diese constraint languages hätten / gibt es weitere hypothesen? - alles was in der tabelle auffällig ist / normaliisert über die datensatzgröße / 3 sehr wichtige und repräsentative vokabulare im sbe bereich / interessanate constraints mit ausreißern / hypothesen über weitere vokabulare müssen verifiziert oder falsifiziert werden / diskussion: / 3 constraints werden zufällig nie verletzt / basis für future work / motivation, dass man constraint languages entwicken muss die complexe constraints abbilden / datenqualität ist generell sehr hoch / als hypothese postulieren}

-----

\begin{hyp}

\end{hyp}

We hypothesise

-----

As the number of evaluated triples differs between the vocabularies, the stated total values are normalized percentage values.

-----

Disco is a new vocabulary which is published in 2015

for this vocabulary the published data is not consistent with the vocabulary

-----

We have to be careful making general statements for all vocabularies as we evaluate only 3 vocabularies

-----

future work:
To make general statements for all vocabularies, we will evaluate data sets of more vocabularies

-----

More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints (see table \ref{tab:evaluation-constraint-violations}).
The majority (86.7\%) of the constraint violations are caused by $\mathcal{CT}_{C}$ constraints and only 9\% by $\mathcal{CT}_{S}$ constraints.
The fact that only 4\% of all constraint violations result from $\mathcal{CT}_{B}$ constraints, 
even though, more than 50\% of all constraints are $\mathcal{CT}_{B}$ constraints,
is an indicator that data producers achieve good data quality with respect to the constraints extracted by vocabularies.
Two-thirds of the constraint violations, thrown for \emph{Disco} data sets, result from $\mathcal{CT}_{B}$ constraints,
almost only $\mathcal{CT}_{C}$ constraints raised constraint violations for \emph{QB} data sets, and 
nearly 80\% of the \emph{SKOS} constraint violations are caused by $\mathcal{CT}_{S}$ constraints.
Although, only 8.5\% of all constraints are $\mathcal{SL}_{1}$ constraints,
9 0f 10 constraint violations are caused by constraints associated with the default severity level $\mathcal{SL}_{1}$.
More than 50\% of all constraint violations thrown for \emph{Disco} data sets are not seen to be that significant ($\mathcal{SL}_{0}$).
Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are classified as warnings ($\mathcal{SL}_{1}$).  
As this evaluation serves as indication for \emph{good} or \emph{bad} (meta)data quality, 
we conclude that
the metadata quality of all evaluated \emph{Disco} data sets is \emph{good} and that the metadata quality of all evaluated \emph{QB} and \emph{SKOS} data sets is \emph{satisfactory}.
%The constraints responsible for the largest amounts of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916; \emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; \emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; \emph{SKOS}).

-----

\begin{hyp}
More than the half of the vocabulary constraints are associated with the severity level error and
more than 3/4 of the simple constraints are only informational constraints. 
\end{hyp}
Table \ref{tab:evaluation-complexity-severity} shows the relation between the complexity and the severity level of all 213 constraints.

@@

>>>>

In this paper, we formulate 246 constraints of 53 different types on six different vocabularies (Disco, QB, SKOS, PHDD, DCAT, XKOS) and classify them according to the complexity level of their type and their severity level. For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.

@@

	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$). 
In close collaboration with several \emph{SBE} domain experts, we defined 246 constraint 
of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classifies them according to the complexity level of their type and their severity level. 
For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
These vocabularies are the central and most representative ones within the \emph{SBE} community. 
We distinct two classes of vocabularies: 
(1) established vocabularies which are widely adopted and accepted and 
(2) newly developed vocabularies which are either recently published or are still in the publication process.
It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
and that early adopters did not properly understand its formal specification.
We investigate the quality of data conforming to the established vocabularies \emph{QB} and \emph{SKOS} and to the newly developed vocabulary \emph{Disco} which will be published in 2015.

We evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.

We validated 
9,990 / 3,775,983,610 (\emph{QB}),
4,178 / 477,737,281 (\emph{SKOS}), and 
1,526 / 9,673,055 (\emph{Disco}) data sets / triples using the \emph{RDF Validator} in batch mode.
That are more than 4.2 billion triples and 15 thousand data sets.
We validated, i.a., 
(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics (ABS)},
the \emph{European Central Bank (ECB)}, and the
\emph{Organisation for Economic Co-operation and Development (OECD)},
(2) \emph{SKOS} thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
the \emph{STW Thesaurus for Economics}, and the
\emph{Thesaurus for the Social Sciences (TheSoz)}, and
(3) \emph{Disco} data sets provided by the \emph{Microdata Information System (Missy)}, 
the \emph{DwB Discovery Portal}, the
\emph{Danish Data Archive (DDA)}, and the
\emph{Swedish National Data Service (SND)}.
We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as second appendix of this paper) 
in which we describe the comprehensive evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.

Based on this evaluation we formulate hypotheses.
Nevertheless, we have to be careful making general statements for all vocabularies 
as these hypotheses still have to be verified or falsified in terms of future work 
by evaluating the quality of data represented by additional established and newly developed vocabularies.

@@

%DCAT: 11 constraints defined
%PHDD: 12
%XKOS: 10

%The majority (48 $\equiv$ 58.5\%) of the overall 82 $\mathcal{CT}$ constraint types are $\mathcal{CT}_{B}$ whose constraints can therefore be derived from vocabularies without any effort.
%Among $\mathcal{CT}_{B}$, two-thirds (34 $\equiv$ 70.8\%) are $\mathcal{C}_B ^{\mathcal{R}}$, i.e., constraint types for which reasoning may be performed prior to validation, and one third (14 $\equiv$ 29.2\%) are $\overline{\mathcal{C}_B ^{\mathcal{R}}}$, i.e., constraint types for which reasoning does not make any sense.
%A quarter (20 $\equiv$ 24.4\%) of all constraint types are $\mathcal{CT}_{S}$ and a sixth (14 $\equiv$ 17.1\%) are $\mathcal{CT}_{C}$.
%
%\begin{table}[H]
		%\scriptsize
    %\begin{center}
    %\begin{tabular}{@{}lcccc@{}}
%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%%    \\  \cmidrule{2-7}
    %\\       \textbf{Criteria}
           %& \textbf{\emph{Disco}}
           %& \textbf{\emph{QB}}
					 %& \textbf{\emph{SKOS}}
					 %& \textbf{Total}
    %\\ \midrule
		%%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
		%%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
		%%\hline
		%\emph{CT} & 52 & 20 & 15 & 53 \\
		%\hline
		%$\mathcal{CT}_{C}$ & 9 (17.3\%) & 2 (10\%) & 2 (13.3\%) & 9 (17\%) \\
		%$\mathcal{CT}_{S}$ & 16 (30.8\%) & 3 (15\%) & 4 (26,7\%) & 16 (30.2\%) \\
		%$\mathcal{CT}_{B}$ & 27 (\textbf{51.9\%}) & 15 (\textbf{75\%}) & 9 (\textbf{60\%}) & 28 (\textbf{52.8\%}) \\
		%\hline
		%$\mathcal{C}_B ^{\mathcal{R}}$ & 18 (34.6\%) & 9 (45\%) & 4 (26.7\%) & 19 (35.9\%) \\
		%$\overline{\mathcal{C}_B ^{\mathcal{R}}}$ & 9 (17.3\%) & 6 (30\%) & 5 (33.3\%) & 9 (17\%) \\
    %\bottomrule
    %\end{tabular}
    %%\\ \emph{C (constraints), CT (constraint types)}
    %\caption{Evaluation - Constraint Types}
		%\label{tab:evaluation-constraint-types}
    %\end{center}
%\end{table}

%Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
Table \ref{tab:evaluation-constraint-violations} shows the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent.
The constraints and their resulting constraint violations are grouped by vocabulary, complexity level of their type, and severity level.
The number of evaluated triples and data sets differs between the vocabularies
as we evaluated 3.8 billion QB, 480 million SKOS, and 10 million Disco triples.
In order to get suitable statements for all vocabularies,  
we normalize the total values which apply for all vocabularies
by building the arithmetic mean over the individual vocabularies' percentage values.

@@

More than the half of them are $\mathcal{CT}_{B}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
For \emph{Disco}, \emph{QB}, and \emph{SKOS}, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
(for \emph{QB} even three quarters).
\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
Half of the overall 213 $\mathcal{CT}$ constraints are $\mathcal{CT}_{B}$ constraints (almost 40\% $\mathcal{C}_B ^{\mathcal{R}}$).
This is not surprising as more than the half of the instantiated constraints types are $\mathcal{CT}_{B}$ constraint types.
More than 50\% of the \emph{Disco} and \emph{QB} constraints are $\mathcal{CT}_{B}$ constraints.
The \emph{SKOS} constraints, on the other side, are equally assigned to the three disjoint constraint type sets. 
More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints (see table \ref{tab:evaluation-constraint-violations}).
The majority (86.7\%) of the constraint violations are caused by $\mathcal{CT}_{C}$ constraints and only 9\% by $\mathcal{CT}_{S}$ constraints.
The fact that only 4\% of all constraint violations result from $\mathcal{CT}_{B}$ constraints, 
even though, more than 50\% of all constraints are $\mathcal{CT}_{B}$ constraints,
is an indicator that data producers achieve good data quality with respect to the constraints extracted by vocabularies.
Two-thirds of the constraint violations, thrown for \emph{Disco} data sets, result from $\mathcal{CT}_{B}$ constraints,
almost only $\mathcal{CT}_{C}$ constraints raised constraint violations for \emph{QB} data sets, and 
nearly 80\% of the \emph{SKOS} constraint violations are caused by $\mathcal{CT}_{S}$ constraints.
\begin{hyp}
A significant amount of 47\% of the violations refer to complex constraints that are not easily expressible in existing languages which confirms the necessity to provide suitable constraint languages.
\end{hyp} 
These days, vocabulary and simple constraints can be easily, concisely, and intuitively expressed by either modeling languages (e.g., RDF, RDFS, OWL 2) or constraint languages (e.g., ShEx, ReSh, and SPIN). 
This is not the case, however, for complex constraints which still have to be expressed by plain SPARQL. 
There is a huge motivation to extend existing constraint languages or to develop new constraint languages which enable to express complex constraints
As a consequence, being able to express complex constraints more easily, concisely, and intuitively leads to significant improvements in data quality.

Data quality is not bad since only a small amount of the constraint violations are caused by error constraints
\emph{SBE} domain experts associated almost the half of the constraints with the severity levels $\mathcal{SL}_{0}$ (\emph{informational}) (47\%) and $\mathcal{SL}_{2}$ (\emph{error}) (45\%);
only 8.5\% are $\mathcal{SL}_{1}$ (\emph{warning}) constraints.
The violation of 80\% of the \emph{QB} constraints is very serious ($\mathcal{SL}_{2}$).
More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are assigned to the weakest default severity level ($\mathcal{SL}_{0}$).
For Disco, 1/6 of the constraint violations are serious.
Although, only 8.5\% of all constraints are $\mathcal{SL}_{1}$ constraints,
9 0f 10 constraint violations are caused by constraints associated with the default severity level $\mathcal{SL}_{1}$.
More than 50\% of all constraint violations thrown for \emph{Disco} data sets are not seen to be that significant ($\mathcal{SL}_{0}$).
Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are classified as warnings ($\mathcal{SL}_{1}$).  
As this evaluation serves as indication for \emph{good} or \emph{bad} (meta)data quality, 
we conclude that
the metadata quality of all evaluated \emph{Disco} data sets is \emph{good} and that the metadata quality of all evaluated \emph{QB} and \emph{SKOS} data sets is \emph{satisfactory}.
\begin{hyp}
In general, data quality is very high.
The quality of data represented by established vocabularies is good,
as serious constraint violations rarely appear.
The quality of data represented by newly developed vocabularies, however, is worse,
as serious constraint violations occur partially.
For well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
\end{hyp}

\begin{hyp}
The percentage of severe constraint violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
\end{hyp}

%For the vocabularies \emph{Disco}, \emph{QB}, and \emph{SKOS}, we defined 213 constraints of 53 constraint types .

%\begin{table}[H]
		%\scriptsize
    %\begin{center}
    %\begin{tabular}{@{}lcccc@{}}
%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%%    \\  \cmidrule{2-7}
    %\\       \textbf{Criteria}
           %& \textbf{\emph{Disco}}
           %& \textbf{\emph{QB}}
					 %& \textbf{\emph{SKOS}}
					 %& \textbf{Total}
    %\\ \midrule
		%%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
		%%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
		%%\hline
		%\emph{C} & 143 (67.1\%) & 35 (16.4\%) & 35 (16.4\%) & 213 \\
		%\hline
		%\emph{C (}$\mathcal{CT}_{C}$\emph{)} & 37 (25.9\%) & 13 (37.1\%) & 13 (\textbf{37.1\%}) & 63 (29.6\%) \\
		%\emph{C (}$\mathcal{CT}_{S}$\emph{)} & 28 (19.6\%) & 3 (8.6\%) & 12 (\textbf{34.3\%}) & 43 (20.2\%) \\
		%\emph{C (}$\mathcal{CT}_{B}$\emph{)} & 78 (\textbf{54.6\%}) & 19 (\textbf{54.3\%}) & 10 (\textbf{28.6\%}) & 107 (\textbf{50.2\%}) \\
		%%\hline
		%%\emph{C (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 67 (46.9\%) & 13 (37.1\%) & 4 (11.4\%) & 84 (39.4\%) \\
		%%\emph{C (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 11 (7.7\%) & 6 (17.1\%) & 6 (17.1\%) & 23 (10.8\%) \\
		%\hline
		%\emph{C ($\mathcal{SL}_{0}$)} & 75 (\textbf{52.5\%}) & 4 (11.4\%) & 21 (\textbf{60\%}) & 100 (\textbf{46.9\%}) \\
		%\emph{C ($\mathcal{SL}_{1}$)} & 10 (7\%) & 3 (8.6\%) & 5 (14.3\%) & 18 (8.5\%) \\
		%\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.6\%) & 28 (\textbf{80\%}) & 9 (25.7\%) & 95 (\textbf{44.6\%}) \\
    %\bottomrule
    %\end{tabular}
    %%\\ \emph{C (constraints), CT (constraint types)}
    %\caption{Evaluation - Constraints}
		%\label{tab:evaluation-constraints}
    %\end{center}
%\end{table}

@@

\tb{difference between 0\% and 78.6\%}

\tb{it has to be ensured that constraints within a particular set are not violated randomly  
in case there are only a few constraints within a set}

\tb{established vocabularies meet vocabulary constraints / data sets represented by established vocabularies meet vocabulary constraints which indicates good data quality}

\tb{QB data sets contain data and metadata and therefore there are the differences between constraint violations}

%The constraints responsible for the largest amounts of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916; \emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; \emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; \emph{SKOS}).

Table \ref{tab:evaluation-complexity-severity} shows the relation between the complexity and the severity level of all 213 constraints.

@@

\begin{hyp}
More than the half of the vocabulary constraints are associated with the severity level error and
more than 3/4 of the simple constraints are only informational constraints. 
\end{hyp}
